---
title: "P8105 - Homework 1"
author: "Chenxi Liu"
date: 9/13/2020
output: github_document
---

```{r load tidyverse libraray, message = FALSE}
library(tidyverse)
```

# Problem 1

Create a data frame
```{r}
problem1_df = tibble(
   vec_numeric = rnorm(10),
   vec_logical = vec_numeric > 0,
   vec_char = c("My", "name", "is", "Chenxi", "I", "like", "doing", "data", "science", "peroid"), 
   vec_factor = factor(c("lv1", "lv1", "lv3", "lv2", "lv1", "lv2", "lv3", "lv2", "lv3", "lv2"))
)
problem1_df
```

Try to take the mean of each variable in problem1_df
```{r, warning = FALSE}
mean(pull(problem1_df, vec_numeric))
mean(pull(problem1_df, vec_logical))
mean(pull(problem1_df, vec_char))
mean(pull(problem1_df, vec_factor))
```
I got numeric result for the numeric and logical factors. I got NA for character and factor vectors since they are not numeric. 


Apply the as.numeric function to the logical, character, and factor variables.
```{r, eval = FALSE}
as.numeric(pull(problem1_df, vec_logical))
as.numeric(pull(problem1_df, vec_char))
as.numeric(pull(problem1_df, vec_factor))

mean(as.numeric(pull(problem1_df, vec_logical)))
mean(as.numeric(pull(problem1_df, vec_char)))
mean(as.numeric(pull(problem1_df, vec_factor)))
```
The mean for character vector is still NA. The mean for logical vector is still 0.6. However, each level of factor was intepreted as 1, 2 , 3. The mean of factor vector become 2.

```{r, warning = FALSE}
as.numeric(pull(problem1_df, vec_logical)) * pull(problem1_df, vec_numeric)
as.factor(pull(problem1_df, vec_logical)) * pull(problem1_df, vec_numeric)
as.numeric(as.factor(pull(problem1_df, vec_logical))) * pull(problem1_df, vec_numeric)
```


# Problem 2
Load the penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
str(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```
This dataset has variables of species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year.
It has 344 rows and 8 columns. The mean flipper length is 200.9mm. 

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, shape = species, color = species)) + geom_point()
ggsave("penguins_scatterplots.png")
```




