---
title: "P8105 - Homework 1"
author: "Chenxi Liu"
date: 9/13/2020
output: github_document
---

# Problem 1

```{r load tidyverse libraray, message = FALSE}
library(tidyverse)
```


Create a data frame
```{r}
problem1_df = tibble(
   vec_numeric = rnorm(10),
   vec_logical = vec_numeric > 0,
   vec_char = c("My", "name", "is", "Chenxi", "I", "like", "doing", "data", "science", "peroid"), 
   vec_factor = factor(c("lv1", "lv1", "lv3", "lv2", "lv1", "lv2", "lv3", "lv2", "lv3", "lv2"))
)
problem1_df
```

Try to take the mean of each variable in problem1_df
```{r, warning = FALSE}
mean(problem1_df[["vec_numeric"]])
mean(problem1_df[["vec_logical"]])
mean(problem1_df[["vec_char"]])
mean(problem1_df[["vec_factor"]])
```
I got numeric result for the numeric and logical factors. I got NA for character and factor vectors since they are not numeric. 


Apply the as.numeric function to the logical, character, and factor variables.
```{r, eval = FALSE}
as.numeric(problem1_df[["vec_char"]])
as.numeric(problem1_df[["vec_logical"]])
as.numeric(problem1_df[["vec_factor"]])

mean(as.numeric(problem1_df[["vec_char"]]))
mean(as.numeric(problem1_df[["vec_logical"]]))
mean(as.numeric(problem1_df[["vec_factor"]]))
```
The mean for character vector is still NA. The mean for logical vector is still 0.6. However, each level of factor was intepreted as 1, 2 , 3. The mean of factor vector become 2.

```{r, warning = FALSE}
as.numeric(problem1_df[["vec_logical"]]) * problem1_df[["vec_numeric"]]
as.factor(problem1_df[["vec_logical"]]) * problem1_df[["vec_numeric"]]
as.numeric(as.factor(problem1_df[["vec_logical"]])) * problem1_df[["vec_numeric"]]
```


# Problem 2
Load he penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```

